### 2013-10-06 src2/papp/paperThesis.tex
apa
hacking

\subsection*{Abstract}
Obsidian is a domain specific language for data-parallel programming 
on graphics processors (GPUs). It is embedded in the functional 
programming language Haskell. The user writes code using constructs 
familiar from Haskell (like {\tt map} and {\tt reduce}), recursion 
and some specially designed combinators for combining GPU programs. 
NVIDIA CUDA code is generated from these high level descriptions, and 
passed to the {\tt nvcc} compiler~\cite{CUDAGuide2.0}. Currently, we 
consider only the generation of single kernels, and not their coordination.

@@

%Obsidian is a domain specific language for Data-parallel 
%programming on graphics processors (GPUs) embedded in Haskell. 
%From high level descriptions, code for execution on a GPU is generated.
%Obsidian generates NVIDIA CUDA code that is passed to the {\tt nvcc} 
%compiler \cite{CUDAGuide2.0}.

%This paper is mainly focused on the usage of Obsidian. The implementation
%of Obsidian itself and a discussion of how the CUDA code is generated can 
%be found in \cite{JSTECH}.

@@

Multicore and manycore processors are becoming increasingly common. Modern 
graphics processing units (GPUs) are examples of manycore processors. Today 
GPUs come with hundreds of processing elements capable of managing thousands 
of threads \cite{Brief8800}. The Obsidian project is about exploring ways 
to program these new machines.

Obsidian is a domain specific language for general purpose programming on 
GPUs (GPGPU), capable of generating code for modern NVIDIA GPUs. 
In~\cite{JSMSKC_IFL08} we describe a version of Obsidian that uses a monadic 
interface. In the current version of Obsidian the monad has been replaced 
by another data structure, closely related to Arrows~\cite{Arrows}, representing GPU programs. Although the details are 
left out because of space limitations, the use of this GPU program representation 
can be seen in subsection~\ref{sec:GPUPrograms}. For a description of the implementation 
see~\cite{JSTECH} and for more general information on embedded language 
implementation see~\cite{COMPILEEDSL}.

GPU design is driven by the performance demands of graphics applications. 
The kind of processing that is common in graphics falls in the data-parallel 
category \cite{GEMS2}.
% One example of a computation from graphics is the 
%transformation of vertices between different coordinate systems. That is, 
%each vertex is multiplied by the same transformation matrix, fitting  the 
%data-parallel paradigm perfectly.

@@

Starting with the 8000 series of GPUs (the G80 architecture), NVIDIA's 
GPUs came with a unified architecture, meaning that all the 
processing elements on the GPU are of the same kind. This was different from 
the previous generation's GPUs, which typically had two kinds of 
processing elements, fragment and vertex processors.  
%There was one kind of processor designed to process fragment/pixel programs and another to process vertex data. 
Now these two kinds 
of processors are replaced by a single kind with capabilities surpassing both 
of the old ones. This new unified architecture together with development tools 
for GPGPU programming go under the 
name CUDA (Compute Unified Device Architecture) 
\cite{CUDAGuide2.0}. CUDA offers the GPGPU programmer a C %,wwwcuda,Brief8800
compiler and libraries for CUDA enabled GPUs (NVIDIA 8000 series and above).

@@

Each MP is capable of maintaining a large number of threads in flight at the 
same time. A group of threads running on an MP is referred to as a {\em block}. 
A block can contain more threads then there are processing elements; today a 
block can hold up to 1024 threads. There is a scheduler mapping these threads 
over the SPs available. Threads are scheduled in groups called {\em warps} 
consisting of 32 threads that are executed in an SIMD fashion on the MPs.
Conditionals that take different paths within a warp have a negative effect 
on performance; the two diverging paths will in fact be executed sequentially 
\cite{BestPrac}.
%There are however, more threads in a
%warp then there are SPs, so the SPs are switching threads to work on 
%between every instruction. This means that conditionals that
%take different paths within a warp have a negative effect on performance;
%the two diverging paths will in fact be executed sequentially \cite{BestPrac}.

@@

Obsidian is a language for GPGPU programming embedded in Haskell. Many of 
the language features resemble those of Lava, a hardware description and 
verification language \cite{lavaICFP}. The justification to use language 
constructs similar to that of a hardware description language came from 
the observation that GPGPU algorithms often were explained using circuit-like 
pictures, see for example \cite{GEMS3}.

%Obsidian can be used to describe hardware like algorithms. These are algorithms
%where the number of inputs and outputs are fixed, not dependent on 
%the values of inputs. 
%There are a large number of algorithms falling into this category. For example, 
%there are numerous sorting algorithms (sorting networks) and parallel prefix 
%algorithms implementable in this way. Also, there are examples in the 
%literature where GPGPU programmers implement their kernels to operate on very 
%specific array sizes \cite{GEMS3}. In a later stage, when the kernels are 
%composed into algorithms on large arrays, support for variable length 
%arrays is introduced.

@@

\begin{small}
\begin{verbatim} 
data a :-> b = ... 
\end{verbatim}
\end{small} 
\noindent
%The details of {\tt a :-> b} are shown in subsection~\ref{sec:Implementation}. 
\noindent
Informally we can think of {\tt a\nolinebreak~:->\nolinebreak~b} as representing programs that operate 
as illustrated in figure~\ref{fig:program}. This figure 
shows a program that performs some computation using a number of threads 
followed by a barrier synchronisation, and so on. The contents of the 
boxes marked with {\em Pure} can be thought of as containing an array 
program.% such as those in subsection~\ref{sec:ArrayLanguage}.
The type constructor {\tt :->} is a variant of an arrow, which in turn is a generalisation of a monad~\cite{JSTECH}.
%
\begin{figure}
\begin{center}
\includegraphics[width=.60\linewidth]{./papp/pictures/prg_intuit.jpg}
\caption{A GPU program of type  {\tt a :-> b} can be thought 
of as pure computations interspersed by syncs.}
\label{fig:program}
\end{center}
\end{figure}
\noindent
One way to create a GPU program is by using the function {\tt pure} of type {\tt (a -> b) -> a :-> b}.
%\begin{small}
%\begin{verbatim}
%pure :: (a -> b) -> a :-> b
%\end{verbatim}
%\end{small}
For example the array language program {\tt fmap (+1)}, that increments 
every element of an array, can be lifted to a GPU program: 
%
\begin{small}
\begin{verbatim}
incr :: Arr IntE :-> Arr IntE 
incr = pure $ fmap (+1)
\end{verbatim}
\end{small} 
 \noindent
GPU programs can be executed on the GPU from
{\em GHCi} (the Haskell interpreter) using the function {\tt execute}:

@@

Sorting is a popular function to place on the GPU, see~\cite{SINTORNSORT,SORT3}.
{\em Odd-Even merge sort}, due to Batcher, uses a merger component called the Odd-Even merger. This 
merger merges two sorted arrays. In Obsidian this merger and sorter 
can be implemented using the combinators {\tt two}, {\tt ilv}, {\tt evens}
and {\tt odds}. For a detailed description of these combinators see
~\cite{LAVASORTER}.

@@

*Obsidian> execute GPU (mergeOE 3 cmp) ([1,3,5,7,2,4,6,8] :: [IntE]) 
[1,2,3,4,5,6,7,8]
\end{verbatim}
\end{small}
\noindent
Given this merger, the sorter is implemented by recursively sorting 
two halves of the input array followed by an application of the merger:

@@

This subsection shows the implementation of a parallel prefix (also called scan) 
kernel, known as {\tt sklansky} after J. Sklansky \cite{Sklansky}.
This kernel will then be optimised step-by-step using Obsidian. This 
optimisation effort uses an experimental feature of Obsidian called {\tt syncHow}. 
This is different from the normal {\tt sync} in the way it assigns work to threads. 
For a more thorough explanation of {\tt syncHow} see ~\cite{JSTECH}.
For an explanation of the parallel-prefix operation see~\cite{BlellochTR90}.

@@

The Sklansky kernels given above can be used in an algorithm that computes 
the parallel prefix of a large array. This is done in the same way as in
~\cite{ScanCUDA}.
The table below shows the results of using the different parallel prefix 
kernels from above in an algorithm for computing the prefix sums of 
$2^{20}$ elements.

@@

The table above shows the running times of six different Sklansky kernels. 
All runtime measurements where performed on an NVIDIA 9800GX2 using one GPU. 
The code labeled {\em Hand Optimised} was written directly in CUDA. 
This kernel was the result of two afternoons of optimisation effort by 
two people. The three following kernels {\em sklansky} to {\em sklansky2} are 
generated from the given Obsidian programs. The version called {\em sklansky3} 
is identical to {\tt sklansky2} except is in-place. Even the very first version, 
{\em sklansky} performs reasonably well, but by using the experimental features 
the performance can be pushed quite close to the hand optimised version.  
The fastest kernel, called {\em NVIDIA SDK}, is the one supplied 
with the CUDA SDK. This kernel is based on the Brent-Kung network and its 
implementation is shown in~\cite{ScanCUDA}. The {\tt NVIDIA SDK} 
kernel is highly optimized with regards to its memory access pattern and 
so the code is considerably more complicated than that of any of the Obsidian parallel-prefix kernels.

@@

The CUDA code generated by Obsidian uses very few registers. In fact,
the generated code is under-utilizing the resources of the GPU. The generated 
code also contains many common subexpressions. This hints that applying a 
step of common subexpression elimintaion would be beneficial, increasing 
the register use and reducing the repeated computation of values. Performing
common subexpression elimination would also lower the instruction count,
which is quite high to begin with, because loops are unrolled. 
The register usage and instruction count values on which these conclusions 
are based where obtained using the CUDA profiler supplied as part of the 
CUDA toolkit~\cite{wwwcuda}.

@@

GPUs are becoming more and more interesting to use in non-graphical applications.
A modern GPU is a manycore machine with, today, hundreds of processing elements. 
The question of how to program these machines arises. NVIDIA's answer is CUDA
\cite{CUDAGuide2.0}. CUDA supplies a slightly extended version of C in which 
the programmer can specify GPU kernels and the controlling CPU program in the 
same language. In CUDA the programmer writes a single program parameterised 
over a thread identity. Compare this to Obsidian where the program describes 
a computation over an array.

There are a number of other C/C++ based languages that target 
GPGPU programmers, for example Brook\cite{Brook} and 
RapidMind\cite{RapidMind}. Brook, CUDA and RapidMind are major improvements from 
what was previously available for the programmer interested in general purpose 
computations on the GPU. 
%Before these, the GPGPU programmer only had the 
%graphics API to work with and needed to translate his or her programs into 
%graphics vocabulary in order to use the GPU.

Higher level approaches are also being investigated. PyGPU embedds a GPGPU 
programming language in Python\cite{PyGPU}. PyGPU makes use of Python's 
introspective abilities to generate efficient code.

Like Obsidian, Accelerate is embedded in Haskell \cite{GPUGEN}. Accelerate 
however, is higher level language than Obsidian. Where the purpose of 
Obsidian is to implement basic algorithmic building blocks such as 
reductions and prefix sums, Accelerate provide these building blocks as 
primitives.

Vertigo is another GPU programming language embedded in Haskell\cite{VERTIGO}.
Vertigo can be used to describe procedureal surfaces and textures and generates
efficient DirectX9 shader code.

There are also many examples of domain specific languages (DSLs)
that target not only GPUs but also other platforms, such as multicore machines.
Of particular interest to us is Microsoft's Accelerator project~\cite{ACCELERATOR}. Interestingly, Accelerator includes the same restriction to ``hardware-like'' algorithms as Obsidian does.
%However, Vertigo is targeting graphical applications.

%There are also many examples of languages that do not specifically target 
%GPUs but experiment with new methods and ways of parallel programming. 
%In this category we have Sequoia, where the memory hierarchy is in focus. 
%Sequoia programs can for example be compiled to the Cell BE architecture. 
%Data-Parallel Haskell extends Haskell with parallel arrays and operations 
%on parallel arrays\cite{DPH}. Data-Parallel Haskell implements the nested 
%data-parallel paradigm and is in that sense following in the path of 
%NESL\cite{NESL}.

%\begin{itemize}
%\item Chapel \cite{Chapel}
%\item DPH \cite{DPH}
%\item Fortress \cite{fortress}
%\item GPUGen \cite{GPUGEN}
%\item Lava \cite{lavaTutorial}
%\item RapidMind \cite{RapidMind}
%\item Sequoia \cite{SEQUOIA}
%\item X10 \cite{X10}
%\end{itemize}

@@

%\bibliographystyle{elsarticle-num}
%\bibliography{obs_okt}

>>>>

\subsection*{Abstract}
Obsidian is a domain specific language for data-parallel programming 
on graphics processors (GPUs). It is embedded in the functional 
programming language Haskell. The user writes code using constructs 
familiar from Haskell (like {\tt map} and {\tt reduce}), recursion 
and some specially designed combinators for combining GPU programs. 
NVIDIA CUDA code is generated from these high level descriptions, and 
passed to the {\tt nvcc} compiler~\citepapp{CUDAGuide2.0}. Currently, we 
consider only the generation of single kernels, and not their coordination.

@@

%Obsidian is a domain specific language for Data-parallel 
%programming on graphics processors (GPUs) embedded in Haskell. 
%From high level descriptions, code for execution on a GPU is generated.
%Obsidian generates NVIDIA CUDA code that is passed to the {\tt nvcc} 
%compiler \citepapp{CUDAGuide2.0}.

%This paper is mainly focused on the usage of Obsidian. The implementation
%of Obsidian itself and a discussion of how the CUDA code is generated can 
%be found in \citepapp{JSTECH}.

@@

Multicore and manycore processors are becoming increasingly common. Modern 
graphics processing units (GPUs) are examples of manycore processors. Today 
GPUs come with hundreds of processing elements capable of managing thousands 
of threads \citepapp{Brief8800}. The Obsidian project is about exploring ways 
to program these new machines.

Obsidian is a domain specific language for general purpose programming on 
GPUs (GPGPU), capable of generating code for modern NVIDIA GPUs. 
In~\citepapp{JSMSKC_IFL08} we describe a version of Obsidian that uses a monadic 
interface. In the current version of Obsidian the monad has been replaced 
by another data structure, closely related to Arrows~\citepapp{Arrows}, representing GPU programs. Although the details are 
left out because of space limitations, the use of this GPU program representation 
can be seen in subsection~\ref{sec:GPUPrograms}. For a description of the implementation 
see~\citepapp{JSTECH} and for more general information on embedded language 
implementation see~\citepapp{COMPILEEDSL}.

GPU design is driven by the performance demands of graphics applications. 
The kind of processing that is common in graphics falls in the data-parallel 
category \citepapp{GEMS2}.
% One example of a computation from graphics is the 
%transformation of vertices between different coordinate systems. That is, 
%each vertex is multiplied by the same transformation matrix, fitting  the 
%data-parallel paradigm perfectly.

@@

Starting with the 8000 series of GPUs (the G80 architecture), NVIDIA's 
GPUs came with a unified architecture, meaning that all the 
processing elements on the GPU are of the same kind. This was different from 
the previous generation's GPUs, which typically had two kinds of 
processing elements, fragment and vertex processors.  
%There was one kind of processor designed to process fragment/pixel programs and another to process vertex data. 
Now these two kinds 
of processors are replaced by a single kind with capabilities surpassing both 
of the old ones. This new unified architecture together with development tools 
for GPGPU programming go under the 
name CUDA (Compute Unified Device Architecture) 
\citepapp{CUDAGuide2.0}. CUDA offers the GPGPU programmer a C %,wwwcuda,Brief8800
compiler and libraries for CUDA enabled GPUs (NVIDIA 8000 series and above).

@@

Each MP is capable of maintaining a large number of threads in flight at the 
same time. A group of threads running on an MP is referred to as a {\em block}. 
A block can contain more threads then there are processing elements; today a 
block can hold up to 1024 threads. There is a scheduler mapping these threads 
over the SPs available. Threads are scheduled in groups called {\em warps} 
consisting of 32 threads that are executed in an SIMD fashion on the MPs.
Conditionals that take different paths within a warp have a negative effect 
on performance; the two diverging paths will in fact be executed sequentially 
\citepapp{BestPrac}.
%There are however, more threads in a
%warp then there are SPs, so the SPs are switching threads to work on 
%between every instruction. This means that conditionals that
%take different paths within a warp have a negative effect on performance;
%the two diverging paths will in fact be executed sequentially \citepapp{BestPrac}.

@@

Obsidian is a language for GPGPU programming embedded in Haskell. Many of 
the language features resemble those of Lava, a hardware description and 
verification language \citepapp{lavaICFP}. The justification to use language 
constructs similar to that of a hardware description language came from 
the observation that GPGPU algorithms often were explained using circuit-like 
pictures, see for example \citepapp{GEMS3}.

%Obsidian can be used to describe hardware like algorithms. These are algorithms
%where the number of inputs and outputs are fixed, not dependent on 
%the values of inputs. 
%There are a large number of algorithms falling into this category. For example, 
%there are numerous sorting algorithms (sorting networks) and parallel prefix 
%algorithms implementable in this way. Also, there are examples in the 
%literature where GPGPU programmers implement their kernels to operate on very 
%specific array sizes \citepapp{GEMS3}. In a later stage, when the kernels are 
%composed into algorithms on large arrays, support for variable length 
%arrays is introduced.

@@

\begin{small}
\begin{verbatim} 
data a :-> b = ... 
\end{verbatim}
\end{small} 
\noindent
%The details of {\tt a :-> b} are shown in subsection~\ref{sec:Implementation}. 
\noindent
Informally we can think of {\tt a\nolinebreak~:->\nolinebreak~b} as representing programs that operate 
as illustrated in figure~\ref{fig:program}. This figure 
shows a program that performs some computation using a number of threads 
followed by a barrier synchronisation, and so on. The contents of the 
boxes marked with {\em Pure} can be thought of as containing an array 
program.% such as those in subsection~\ref{sec:ArrayLanguage}.
The type constructor {\tt :->} is a variant of an arrow, which in turn is a generalisation of a monad~\citepapp{JSTECH}.
%
\begin{figure}
\begin{center}
\includegraphics[width=.60\linewidth]{./papp/pictures/prg_intuit.jpg}
\caption{A GPU program of type  {\tt a :-> b} can be thought 
of as pure computations interspersed by syncs.}
\label{fig:program}
\end{center}
\end{figure}
\noindent
One way to create a GPU program is by using the function {\tt pure} of type {\tt (a -> b) -> a :-> b}.
%\begin{small}
%\begin{verbatim}
%pure :: (a -> b) -> a :-> b
%\end{verbatim}
%\end{small}
For example the array language program {\tt fmap (+1)}, that increments 
every element of an array, can be lifted to a GPU program: 
%
\begin{small}
\begin{verbatim}
incr :: Arr IntE :-> Arr IntE 
incr = pure $ fmap (+1)
\end{verbatim}
\end{small} 
 \noindent
GPU programs can be executed on the GPU from
{\em GHCi} (the Haskell interpreter) using the function {\tt execute}:

@@

Sorting is a popular function to place on the GPU, see~\citepapp{SINTORNSORT,SORT3}.
{\em Odd-Even merge sort}, due to Batcher, uses a merger component called the Odd-Even merger. This 
merger merges two sorted arrays. In Obsidian this merger and sorter 
can be implemented using the combinators {\tt two}, {\tt ilv}, {\tt evens}
and {\tt odds}. For a detailed description of these combinators see
~\citepapp{LAVASORTER}.

@@

*Obsidian> let input = ([1,3,5,7,2,4,6,8] :: [IntE]) 
*Obsidian> execute GPU (mergeOE 3 cmp) input
[1,2,3,4,5,6,7,8]
\end{verbatim}
\end{small}
\noindent
Given this merger, the sorter is implemented by recursively sorting 
two halves of the input array followed by an application of the merger:

@@

This subsection shows the implementation of a parallel prefix (also called scan) 
kernel, known as {\tt sklansky} after J. Sklansky \citepapp{Sklansky}.
This kernel will then be optimised step-by-step using Obsidian. This 
optimisation effort uses an experimental feature of Obsidian called {\tt syncHow}. 
This is different from the normal {\tt sync} in the way it assigns work to threads. 
For a more thorough explanation of {\tt syncHow} see ~\citepapp{JSTECH}.
For an explanation of the parallel-prefix operation see~\citepapp{BlellochTR90}.

@@

The Sklansky kernels given above can be used in an algorithm that computes 
the parallel prefix of a large array. This is done in the same way as in
~\citepapp{ScanCUDA}.
The table below shows the results of using the different parallel prefix 
kernels from above in an algorithm for computing the prefix sums of 
$2^{20}$ elements.

@@

The table above shows the running times of six different Sklansky kernels. 
All runtime measurements where performed on an NVIDIA 9800GX2 using one GPU. 
The code labeled {\em Hand Optimised} was written directly in CUDA. 
This kernel was the result of two afternoons of optimisation effort by 
two people. The three following kernels {\em sklansky} to {\em sklansky2} are 
generated from the given Obsidian programs. The version called {\em sklansky3} 
is identical to {\tt sklansky2} except is in-place. Even the very first version, 
{\em sklansky} performs reasonably well, but by using the experimental features 
the performance can be pushed quite close to the hand optimised version.  
The fastest kernel, called {\em NVIDIA SDK}, is the one supplied 
with the CUDA SDK. This kernel is based on the Brent-Kung network and its 
implementation is shown in~\citepapp{ScanCUDA}. The {\tt NVIDIA SDK} 
kernel is highly optimized with regards to its memory access pattern and 
so the code is considerably more complicated than that of any of the Obsidian parallel-prefix kernels.

@@

The CUDA code generated by Obsidian uses very few registers. In fact,
the generated code is under-utilizing the resources of the GPU. The generated 
code also contains many common subexpressions. This hints that applying a 
step of common subexpression elimintaion would be beneficial, increasing 
the register use and reducing the repeated computation of values. Performing
common subexpression elimination would also lower the instruction count,
which is quite high to begin with, because loops are unrolled. 
The register usage and instruction count values on which these conclusions 
are based where obtained using the CUDA profiler supplied as part of the 
CUDA toolkit~\citepapp{wwwcuda}.

@@

GPUs are becoming more and more interesting to use in non-graphical applications.
A modern GPU is a manycore machine with, today, hundreds of processing elements. 
The question of how to program these machines arises. NVIDIA's answer is CUDA
\citepapp{CUDAGuide2.0}. CUDA supplies a slightly extended version of C in which 
the programmer can specify GPU kernels and the controlling CPU program in the 
same language. In CUDA the programmer writes a single program parameterised 
over a thread identity. Compare this to Obsidian where the program describes 
a computation over an array.

There are a number of other C/C++ based languages that target 
GPGPU programmers, for example Brook\citepapp{Brook} and 
RapidMind\citepapp{RapidMind}. Brook, CUDA and RapidMind are major improvements from 
what was previously available for the programmer interested in general purpose 
computations on the GPU. 
%Before these, the GPGPU programmer only had the 
%graphics API to work with and needed to translate his or her programs into 
%graphics vocabulary in order to use the GPU.

Higher level approaches are also being investigated. PyGPU embedds a GPGPU 
programming language in Python\citepapp{PyGPU}. PyGPU makes use of Python's 
introspective abilities to generate efficient code.

Like Obsidian, Accelerate is embedded in Haskell \citepapp{GPUGEN}. Accelerate 
however, is higher level language than Obsidian. Where the purpose of 
Obsidian is to implement basic algorithmic building blocks such as 
reductions and prefix sums, Accelerate provide these building blocks as 
primitives.

Vertigo is another GPU programming language embedded in Haskell\citepapp{VERTIGO}.
Vertigo can be used to describe procedureal surfaces and textures and generates
efficient DirectX9 shader code.

There are also many examples of domain specific languages (DSLs)
that target not only GPUs but also other platforms, such as multicore machines.
Of particular interest to us is Microsoft's Accelerator project~\citepapp{ACCELERATOR}. Interestingly, Accelerator includes the same restriction to ``hardware-like'' algorithms as Obsidian does.
%However, Vertigo is targeting graphical applications.

%There are also many examples of languages that do not specifically target 
%GPUs but experiment with new methods and ways of parallel programming. 
%In this category we have Sequoia, where the memory hierarchy is in focus. 
%Sequoia programs can for example be compiled to the Cell BE architecture. 
%Data-Parallel Haskell extends Haskell with parallel arrays and operations 
%on parallel arrays\citepapp{DPH}. Data-Parallel Haskell implements the nested 
%data-parallel paradigm and is in that sense following in the path of 
%NESL\citepapp{NESL}.

%\begin{itemize}
%\item Chapel \citepapp{Chapel}
%\item DPH \citepapp{DPH}
%\item Fortress \citepapp{fortress}
%\item GPUGen \citepapp{GPUGEN}
%\item Lava \citepapp{lavaTutorial}
%\item RapidMind \citepapp{RapidMind}
%\item Sequoia \citepapp{SEQUOIA}
%\item X10 \citepapp{X10}
%\end{itemize}

@@

\bibliographystylepapp{alpha}
\bibliographypapp{thesis}
